---
title: "prep_midterm"
author: "Waranya Ratirotjanakul"
date: 27 Apr 2026
format: html
editor: visual
---

# Workshop5 - Quarto Cross-Referencing and .gitignore Workshop

```{r}
library(ggplot2)
library(palmerpenguins)
```

## Part 1: Cross-Referencing in Quarto
### 1. Referencing Sections

#### Data Cleaning {#sec-cleaning}
See Section @sec-cleaning for details on how the data was prepared.

### 2. Referencing Figures

```{r}
#| label: fig-bill
#| fig-cap: "Bill length vs flipper length"

ggplot(penguins, aes(x = flipper_length_mm, y = bill_length_mm)) +
    geom_point()
```

Figure @fig-bill shows the relationship between flipper length and bill length.

### 4. Referencing Tables

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary statistics of the penguins dataset"

knitr::kable(summary(penguins))
```

See Table @tbl-summary for summary statistics of the dataset.

## Part 2: Ignoring Files with .gitignore

## 📦 Mini Exercise: Using git stash
this is a test for stashing1.
stash testing2

# Workshop 6 - Git Undo Workshop: `git revert` and `git reset`
- `git revert`: Undo a commit by creating a new commit that cancels it out
- `git reset`: Move your branch pointer to a previous commit (⚠️ this can rewrite history!)

# Tutorial 6 - Forking, Branching, and Rebasing with Quarto